Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2018-08-13 workflow/workflow.Rmd
Going back to k=50

```{r}
#save(dataObj, file= 'dataObj_afterZinbwave.rda')
load('dataObj_afterZinbwave.rda')
```

@@

```{r}
#save(dataObj, file = 'dataObj_afterRSEC.rda')
load('dataObj_afterRSEC.rda')
```

>>>>

```{r}
#save(dataObj, file= 'dataObj_afterZinbwave_k10.rda')
load('dataObj_afterZinbwave.rda')
```

@@

```{r}
#save(dataObj, file = 'dataObj_afterRSEC_k10.rda')
load('dataObj_afterRSEC.rda')
```
